README

### 2022-10-26 rmd/supporting_info.Rmd
Update supporting_info.Rmd

---
output:
  bookdown::pdf_document2:
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
mainfont: "Times New Roman"
fontsize: 10.5pt
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{amsmath, fancyhdr, caption, booktabs}
  - \captionsetup{width=1.35\linewidth, labelfont={bf}}
bibliography: reference.bib
csl: https://www.zotero.org/styles/pnas
---

>>>>

---
output:
  bookdown::pdf_document2:
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
mainfont: "Times New Roman"
fontsize: 11pt
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{amsmath, fancyhdr, caption, booktabs}
  - \captionsetup{width=1.35\linewidth, labelfont={bf}}
bibliography: reference.bib
csl: https://www.zotero.org/styles/pnas
---
